\acknowledgements

The authors are grateful for useful suggestions from the CBC group of the LIGO--Virgo Science Collaboration, in particular we are grateful to Walter Del Pozzo for useful advice, Vivien Raymond for helpful discussions, Simon Stevenson for careful reading and Neil Cornish for beneficial comments.

BF was supported by the Enrico Fermi Institute at the University of Chicago as a McCormick Fellow.  This work was supported in part by the Science and Technology Facilities Council. PBG acknowledges NASA grant NNX12AN10G. SV acknowledges the support of the National Science Foundation and the LIGO Laboratory. JV was supported by STFC grant ST/K005014/1. LIGO was constructed by the California Institute of Technology and Massachusetts Institute of Technology with funding from the National Science Foundation and operates under cooperative agreement PHY-0757058.

This work used computing resources at CIERA funded by NSF PHY-1126812, as well as the computing facilities of the LIGO Data Grid including: the Nemo computing cluster at the Center for Gravitation and Cosmology at the University of Wisconsin--Milwauke under NSF Grants PHY-0923409 and PHY-0600953; the Atlas computing cluster at the Albert Einstein Institute, Hannover; the LIGO computing clusters at Caltech, and the facilities of the Advanced Research Computing @ Cardiff (ARCCA) Cluster at Cardiff University.

Some results were produced using the post-processing tools of the \texttt{plotutils} library at \url{http://github.com/farr/plotutils} and \texttt{skyarea} library at \url{https://github.com/farr/skyarea}.

This paper has been assigned LIGO document reference LIGO-P1500117.
  
  
  
  
  
  
  
  